Results

### 2018-11-14 Manuscript_draft/Results.Rmd
plot with figures on it

```{r, echo=FALSE, message=FALSE}
library(vegan)
library(xtable)
library(kableExtra)
library(reshape2)
library(ape)
library(phytools)
#load environment
load("myEnvironment_mantel.RData")
```

@@

```{r, echo=FALSE, message=FALSE, fig.cap="Scatterplot of the evolutive distances (x axis) and the mean scaled effect per species (ITS markers)."}
its_distance <- melt(evo_distance_its)
scaled_effect <- melt(matrix_scale_effect)
scaled_effect$Species=as.character(scaled_effect$Species)
scaled_effect$col_focal[scaled_effect$Species==c("BROL")] <- "red"
scaled_effect$col_focal[scaled_effect$Species==c("BRRA")] <- "red"
scaled_effect$col_focal[scaled_effect$Species==c("SIAL")] <- "red"
scaled_effect$col_focal[scaled_effect$Species==c("ERSA")] <- "red"
scaled_effect$col_focal[scaled_effect$Species==c("SOME")] <- "blue"
scaled_effect$col_focal[scaled_effect$Species==c("SOLY")] <- "blue"
scaled_effect$col_focal[scaled_effect$Species==c("PEIN")] <- "blue"
scaled_effect$col_focal[scaled_effect$Species==c("CAAN")] <- "blue"
scaled_effect$col_focal[scaled_effect$Species==c("IPAQ")] <- "green"
scaled_effect$col_focal[scaled_effect$Species==c("IPPU")] <- "green"
plot(its_distance$value, scaled_effect$value, main="Scatterplot ", 
     xlab="dist", ylab="effect", pch=19, col=scaled_effect$col_focal)
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(vegan)
library(xtable)
library(kableExtra)
library(reshape2)
library(ape)
library(phytools)
library(plotrix)
#load environment
load("myEnvironment_mantel.RData")
```

@@

```{r, echo=FALSE, message=FALSE, fig.cap="Scatterplot of the evolutive distances (x axis) and the mean scaled effect per species (ITS markers)."}
its_distance <- melt(evo_distance_its)
scaled_effect <- melt(matrix_scale_effect)
scaled_effect$Species=as.character(scaled_effect$Species)
scaled_effect$col_focal[scaled_effect$Species==c("BROL")] <- "red"
scaled_effect$col_focal[scaled_effect$Species==c("BRRA")] <- "red"
scaled_effect$col_focal[scaled_effect$Species==c("SIAL")] <- "red"
scaled_effect$col_focal[scaled_effect$Species==c("ERSA")] <- "red"
scaled_effect$col_focal[scaled_effect$Species==c("SOME")] <- "blue"
scaled_effect$col_focal[scaled_effect$Species==c("SOLY")] <- "blue"
scaled_effect$col_focal[scaled_effect$Species==c("PEIN")] <- "blue"
scaled_effect$col_focal[scaled_effect$Species==c("CAAN")] <- "blue"
scaled_effect$col_focal[scaled_effect$Species==c("IPAQ")] <- "green"
scaled_effect$col_focal[scaled_effect$Species==c("IPPU")] <- "green"
plot(its_distance$value, scaled_effect$value, main="Hp effect & evolutive distance", 
     xlab="Pairwise evolutive distances", ylab="Hp effect (Scaled seed set)", pch=19, col=scaled_effect$col_focal)
draw.circle(0.265,0.22,radius=0.045,nv=100,border="red",col=NA,lty=1,density=NULL,angle=45,lwd=1)
draw.circle(0.20,1.8,radius=0.09,nv=100,border="blue",col=NA,lty=1,density=NULL,angle=45,lwd=1)
